\morus: Biases in the Stream

### 2018-05-10 morusAC_06_Discussion.tex
homogenized references
minor consistency fix: MORUS
copyedit

\todo{ME: If this doesn't grow much longer, I'd suggest to make this a subsection of Section 5, and repeat a summary in the Conclusion.}

@@

We now discuss the impact of our attacks for the security of \morus.

@@

However, \cipher{MORUS1280} with a 256-bit key claims a security level
of 256 bits for confidentiality, and an attack with complexity $2^{152}$
should violate this claim, even if it is not practical.  The
\cipher{MORUS} specification limits the amount of plaintext encrypted
with a given key to $2^{64}$, but this does not affect our attack
because we can use keystream generated with different keys.

>>>>

@@

We now discuss the impact of these attacks on the security of \MORUS.

@@

However, \cipher{MORUS1280} with a 256-bit key claims a security level
of 256 bits for confidentiality, and an attack with complexity $2^{152}$
should violate this claim, even if it is not practical.
